Fish do not need visas: the transboundary nature of the world’s exploited marine fish species (79/96 characters)

### 2020-02-11 Manuscript_Draft.Rmd

We overlaid the known distribution of 968 commercially valuable marine species responsable for **XX%** of global catch, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary. First we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g. we did not include the high seas). Secondly, we considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods). The third criteria determined whether a species was exploited within a given grid cell using spatially explicit catch data. A species was considered as present in a grid cell if both predicted species occurrences and catch data were positive. Finally, we determined a spatial threshold based on the proportion of the species' distribution within each neighboring EEZs to confirm occurance in both EEZs.

@@

We identified **633** transboundary exploited species in the world, more than double of previous estimates [@Teh:2015gd], representing **65.4%** of the species analyzed. Transboundary species are partiuclarly abundant in EEZs of western Europe, northwestern Africa, and southeastern Asia (Fig. 1A). Species' composition in these areas is relativly homogenous due to biogeochemical, oceanographic and topography features [@Spalding:2007th; @Reygondeau:2013cd]. For example north west Africa and and west Europe are part of the Lusitanian large marine ecoregion (LME), similarly the Northern European Seas LME and south east China is part of the Western Coral Triangle LME [@Spalding]. Between 2005 and 2014, national fleets targeting shared species within EEZs landed an average of **69.2** million tonnes, representing **64%** of the EEZ-derrived catches, and generating USD **79,745** million in fishing revenue. This is equivalent to **49.8%** of the global fishing revenue of the same period. These values are more than double the 34.2 million t and USD 30,700 million in fishing revenue previously estimated [@Teh:2015gd], underscoring the importance of transboundary species at the global level.

@@

![Fig. 1. Number of transboundary marine species and their contribution to global fisheries catches and revenue. A) The number of species and amount of revenue are represented by colour coding of EEZs and land polygons, respectively. B) Contribution of tranbsoundary species to regional revenue (left) and catch (right). Points = mean +- sd. Revenue in 2010 real USD](./Figures/Fig1.png)

@@

Transboundary species are particularly important economically for Northern America (3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B). China (USD 6,279 million) in E. Asia and the US (USD 9,605 million) in N. America contribute 55% and 83% to their respective region's revenue, respectively. Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with the most fishing revenue generated from transboundary species. These five nations are responsible for 30% of the fishing global revenue from transboundary species. Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5,000 thousand tones each on average between 2005 and 2014 (**Supplemental figure Trans_Catch_MAP**). Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and accounting for 79% of the transboundary species production. Similarly, Russia shares the Alaskan polllock (*Theragra chalcogramma*) fishery with both Japan and the US. Despite the large catch volume of Peru and Russia, regional catches are only significantly different in E. Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followed by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes).

<!-- **NOTE: MAKE SURE RUSSIA IS NOT E.ASIA** -->

>>>>

We overlaid the known distribution of 968 commercially valuable marine species responsable for **95%** of global EEZ catch reported to FAO, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary. First we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g. we did not include the high seas). Secondly, we considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods). The third criteria determined whether a species was exploited within a given grid cell using spatially explicit catch data. A species was considered as present in a grid cell if both predicted species occurrences and catch data were positive. Finally, we determined a spatial threshold based on the proportion of the species' distribution within each neighboring EEZs to confirm occurance in both EEZs.

@@

We identified **633** transboundary exploited species in the world, more than double of previous estimates [@Teh:2015gd], representing **65.4%** of the species analyzed. Between 2005 and 2014, national fleets targeting shared species within EEZs landed an average of **69.2** million tonnes, representing **92%** of the EEZ-derrived catches reported to FAO, and generating USD **79,745** million in fishing revenue. This is equivalent to **49.8% (73.16% according to new numbers)** of the global fishing revenue of the same period. These values are more than double the 34.2 million t and USD 30,700 million in fishing revenue previously estimated [@Teh:2015gd], underscoring the importance of transboundary species at the global level.

@@

![Fig. 1. Number of transboundary marine species and their contribution to global fisheries catches and revenue. A) The number of species and amount of revenue are represented by colour coding of EEZs and land polygons, respectively. B) Contribution of tranbsoundary species to regional revenue (left) and catch (right). Regions according to the United Nations sub-regions. Points = mean +- sd. Revenue in 2010 real USD](./Figures/Fig1.png)

@@

We aggregate countries according to the United Nations sub-regions (**Supplements**) and found that transboundary species are particularly economically important for Northern America (3,901 $\pm$ 4,497 million USD) and Eastern Asia (2,827 $\pm$ = 2,667 million USD), significantly differing from other regions in terms of revenue (one-way ANOVA; *F*(16,157) = 4.91, *p* < 0.001, $\alpha$ = 0.05) (Fig 1B). China (USD 6,279 million) in E. Asia and the US (USD 9,605 million) in N. America contribute 55% and 83% to their respective region's revenue, respectively. Russia (USD 6,361 million), Peru (USD 5,211) and Japan (USD 3,369) complete the top five countries with the most fishing revenue generated from transboundary species. These five nations are responsible for 30% of the fishing global revenue from transboundary species. Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5,000 thousand tones each on average between 2005 and 2014 (**Supplemental figure Trans_Catch_MAP**). Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and accounting for 79% of the transboundary species production. Similarly, Russia shares the Alaskan polllock (*Theragra chalcogramma*) fishery with both Japan and the US. Despite the large catch volume of Peru and Russia, regional catches are only significantly different in E. Asia (one-way ANOVA; *F*(16,155) = 3.341, *p* < 0.001, $\alpha$ = 0.05), with China, the world's top fish producer with 15.3 million tons landed in 2016 [@FAO:2018KK] getting around 1/3 of its capture from transboundary species, followed by Japan (4.2 million tonnes) and South Korea (2.3 million tonnes). Differences in tansboundary fisheries can also be ilustrated in terms of catch-revenue/EEZ $km^2$ (**Supplements_Kmproportion**). As an example, Eastern Europe who's EEZ is the $9^{th}$ larger of the groups analized (**Supplemental table**) shoots out as having the most revenue (XXX) and catch (XXX) of species per EEZ area, significantly differing from the rest (**Statistics**).
